Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-01-10 template.tex
updated analytic signal of detector response proof

The analytic signal of the Askaryan pulse is given by Eq. \ref{eq:sa_4}.  The RLC damped oscillator response and corresponding analytic signal are

@@

r_a(t) &= R_0 e^{-\gamma t} e^{2\pi j f_0 t}

@@

The parameter $\gamma$ is the \textit{decay constant}, and the parameter $f_0$ is the resonance frequency.  Note that the envelope of $r(t)$, $|r_a(t)|$, is simply $R_0 \exp(-\gamma t)$, as it should be.

@@

U(x,t) &= j V(x,t) = \frac{\pi}{4 t} e^{z^2} \erfc(z) \\

>>>>

We should include the proof here (I have to track it down in my notebooks).
\item The analytic signal of the Askaryan pulse is given by Eq. \ref{eq:sa_4}.  The RLC damped oscillator response and corresponding analytic signal are

@@

r_a(t) &= R_0 e^{-\gamma t} e^{2\pi j f_0 t} \label{eq:ra}

@@

The parameter $\gamma$ is the \textit{decay constant}, and the parameter $f_0$ is the resonance frequency.  Note that the envelope of $r(t)$, $|r_a(t)|$, is simply $R_0 \exp(-\gamma t)$, as it should be.  The proof of Eq. \ref{eq:ra} is as follows:
r(t) &= R_0 e^{-\gamma t} \cos(2\pi f_0 t) \\
R(f) &= \frac{R_0}{2\pi j} \left( \frac{f - \frac{j\gamma}{2\pi}}{(f-z_+)(f-z_-)} \right) \\
z_+ &= f_0 + \frac{j\gamma}{2\pi} \\
z_- &= -f_0 + \frac{j\gamma}{2\pi} \\
\widehat{r}(t) &= \mathcal{F}^{-1}\left \lbrace - j \sgn(f) R(f) \right \rbrace \label{eq:rh} \\ 
\widehat{r}(t) &= \frac{R_0}{2j}\left( e^{2\pi j f_0 t} - e^{-2\pi j f_0 t} \right) e^{-\gamma t} \\
\widehat{r}(t) &= R_0 \sin(2\pi f_0 t) e^{-\gamma t} \\
r_a (t) &= R_0 \left(\cos(2\pi f_0 t) + j\sin(2\pi f_0 t)\right) e^{-\gamma t} \\
r_a (t) &= R_0 e^{2\pi j f_0 t} e^{-\gamma t}
In evaluating the inverse Fourier transform in Eq. \ref{eq:rh}, the poles at $z_+$ and $z_-$ must be enclosed in separate contour integrals.

@@

U(x,t) + j V(x,t) &= \sqrt{\frac{\pi}{4 t}} e^{z^2} \erfc(z) \\
